---
title: "Graphical presentation and models' results"
author: "Michael Madin & Kate Nelson"
date: "5/10/2022"
output: html_document
---

This is the codes for the published article. Effects of landscape simplicity on crop yields: A reanalysis of global dataset. Cite this codes as Madin, M. B., & Nelson, K. S. (2023). Effects of landscape simplicity on crop yield: A reanalysis of a global database. Plos one, 18(12), e0289799. Or access the publication at https://doi.org/10.1371/journal.pone.0289799

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo= TRUE, message= FALSE, warning= FALSE)
```

# Required packages 
```{r, echo= F}
library(tidyverse)
library(lme4) # for modeling linear mixed effect
library(lmerTest) # for p-values for lmer
library(sjPlot) # for printing model output
library(sjmisc) # for printing model output
library(sjlabelled) # For printing model output
library(summarytools) # For summary stats
library(sjstats) # estimate partial effect size
library(tmap) # For plotting map
library(ggforce)
library(sf)
library(extrafont) # Text font type
library(MASS) # for ordered Probit Model ('polr()')
```

# Import files

Load merged data comprising production data from Combined pest and pollinator agricultural data (Dainese), climate (WorldClim), and soil (World Harmonized Soil Dataset) data

```{r eval=FALSE, include=FALSE}
# Import Old transformed production dataset by crop type
Merg_PROD1<- read_csv("~/R01_Course_Files/GRA/Merg_PRODzc.csv")
```


## Pre-clean the data

```{r}
# create new column of management practices as published in Dainese et al. paper
Merg_PROD$Manag_Cbin <- Merg_PROD$Manag  

# Group management practices  into organic or conventional
Merg_PROD <- Merg_PROD %>%
  mutate(Manag_Cbin  = ifelse(Manag_Cbin== "Control = monoculture of crop/grasses", "conventional", Manag_Cbin )) %>%
  mutate(Manag_Cbin  = ifelse(Manag_Cbin== "Semi natural habitat lacking a pond", "organic", Manag_Cbin)) %>%
  mutate(Manag_Cbin  = ifelse(Manag_Cbin== "Pond + semi natural habitat", "organic", Manag_Cbin))  


# Change all combined management labels to lower case
Merg_PROD$Manag_Cbin= tolower(Merg_PROD$Manag_Cbin) 


# Change all original management labels to lower case
Merg_PROD$Manag= tolower(Merg_PROD$Manag) 

# add a column to represent dataset 3 (Pollination) and 4 (Pest control)
Merg_PROD<- Merg_PROD%>%
  arrange(desc(ES_PestControl)) ## Sort Pest control dataset first


## Add data rows
Merg_PROD$Study_type<- c(rep("Pest_enemy", 186), rep("Poll_service", 395))

# Rename soil texture class column
Merg_PROD<- Merg_PROD%>%
  rename(Tusda_texcod= Tusda_texCode)
```


# The OLS regression models

## Bi-Linear models

### Yield~ LAND

```{r}
# PROD~ Landscape
Model_lm<- lm(PROD ~ LAND, data = Merg_PROD)

#Print
tab_model(Model_lm, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)
```


### Yield~ Pollination

```{r}
# PROD~ pollination service
Model_lm<- lm(PROD ~ POLL_IND, data = Merg_PROD)

#Print
tab_model(Model_lm, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)
```



### Yield~ PestControl

```{r}
# PROD~ pest control
Model_lm<- lm(PROD ~ ES_PestControl, data = Merg_PROD)

# Print
tab_model(Model_lm, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)

```


### Pollination~ LAND

```{r}
# Pollinator~ Landscape
Model_lm<- lm(POLL_IND ~ LAND, data = Merg_PROD)

#Print
tab_model(Model_lm, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)
```


### PestControl~ LAND

```{r}
# Pest_enemy~ Landscape
Model_lm<- lm(ES_PestControl ~ LAND, data = Merg_PROD)

#Print
tab_model(Model_lm, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)
```



## Interactive models

### Interactive effects of PROD~ landscape and soil texture

```{r}
## Model 2a [Yield]

# Using original management practices in Danise el ta. data
Model_effects<- lm(PROD~ LAND*Manag + AnnualTMax + Precipitation + 
                     Tusda_texnam, data= Merg_PROD)

# Print model output
tab_model(Model_effects, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)


# Get model AIC
AIC(Model_effects)
```



### Interactive effects of PROD~ landscape and management practices

```{r}
# Model 2b [Yield]

Model_effects<- lm(PROD~ LAND*Manag + AnnualTMax + Precipitation + 
                     Tusda_texnam, data= Merg_PROD)

# Print model output
tab_model(Model_effects, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)

#Get model AIC
AIC(Model_effects)
```


### Interactive effects of PROD~ pollination service and management practices

```{r}
## Model 2c [Yield]

# Using original management practices 
Model_effects<- lm(PROD~ POLL_IND*Manag + AnnualTMax + Precipitation + 
                     Tusda_texnam, data= Merg_PROD)


# Print model output
tab_model(Model_effects, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)


#Get model AIC
AIC(Model_effects)
```




### Interactive effects of PROD~ Natural pest control and management practices 
```{r}
# Model 2d [Yield]

Model_effects<- lm(PROD~ ES_PestControl*Manag + AnnualTMax + Precipitation + 
                     Tusda_texnam, data= Merg_PROD)


# Print model output
tab_model(Model_effects, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)


#Get model AIC
AIC(Model_effects)
```



### Interactive effects of POLL_IND~ landscape and Management practices

```{r}
# Model 2e [Pollination]

## Using original management practices in Danise el ta. data

Model_effects<- lm(POLL_IND~ LAND*Manag + AnnualTMax + Precipitation + 
                     Tusda_texnam, data= Merg_PROD)


# Print model output
tab_model(Model_effects, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)


#Get model AIC
AIC(Model_effects)
```



### Interactive effects of ES_PestControl~ landscape and management

```{r}
## Model 2f [Predator [Activity]

# Using original management practices in Danise el ta. data
Model_effects<- lm(ES_PestControl~ LAND*Manag + AnnualTMax + Precipitation + 
                     Tusda_texnam, data= Merg_PROD)

tab_model(Model_effects, p.style = "numeric_stars", digits = 4, digits.p = 3, 
          show.se = TRUE, show.ci = 0.90)

```



## Plots of predicted values

### Model predicted values of crop yields at given landscape simplicity in different soil texture classes (Fig 2.).

```{r}
# Predicted values (marginal effects) for LAND and Soil model terms 90% CI

plot_model(Model_effects, type = "pred", terms = c("LAND", "Tusda_texnam"), 
           line.size = 1.5, ci.lvl = 0.9)+
  ggtitle("")+
  labs(color= "Soil Class")+
  ylab("Standardized crop yield")+
  xlab("Standardized % crop field of 1km radius")+
  scale_linetype_manual(values= c("twodash", "dotted", "solid", "longdash", "dotdash", "dash"))+
  scale_color_manual(labels= c("SCL", "C" , "SL", "L", "S",
                               "LS"), values= c("black", "red", "black", "black",
                                                               "red", "black"))+
  scale_fill_manual(values= c("black", "red", "black", "black",
                                                               "red", "black"))+
  theme_bw()+
  theme(panel.border = element_blank(), 
                        panel.grid.major = element_blank(), 
                        panel.grid.minor = element_blank(),
                        axis.line = element_line(colour = "black"),
                       axis.text = element_text(family = "Times New Roman", 
                                                colour = "black", size = 14),
                       axis.title = element_text(family = "Times New Roman", size = 20),
                       legend.title = element_text(family = "Times New Roman", size = 14),
                       legend.text = element_text(family = "Times New Roman", size = 14))


# Save Image
ggsave("Soil_yield.tiff", width = 10, height = 6, units = "in", dpi = 300)
```



### Model predicted values of natural pest control at given landscape simplicity under different management practices (Fig 3.).

```{r}
# Model predicted values at 90% CI

plot_model(Model_effects, type = "pred", terms = c("LAND", "Manag"), 
           line.size = 1.5, ci.lvl = 0.90)+
  ggtitle("")+
  labs(color= "") +
  ylab("Standardized natural enemy activities")+
  xlab("Standardized % crop field of 1km radius")+
  scale_color_manual(labels= c("Conventional", "Organic"), 
                     values= c("black", "red"))+
  scale_fill_manual(values= c("black", "red"))+
  theme_bw()+
  theme(panel.border = element_blank(), 
                        panel.grid.major = element_blank(), 
                        panel.grid.minor = element_blank(),
                        axis.line = element_line(colour = "black"), 
                        legend.position = ("top"),
                       axis.text = element_text(family = "Times New Roman", 
                                                colour = "black", size = 14),
            axis.title = element_text(family = "Times New Roman", size = 15),
            legend.title = element_text(family = "Times New Roman", size = 14),
            legend.text = element_text(family = "Times New Roman", size = 13))




ggsave("Mgmnt_pest.tiff", width = 8, height = 6, units = "in", dpi = 300)
```


## Plot study location

### Data

```{r}
# Import data

## Convert into sf dataframe
LocationsR_sf<- st_as_sf(LocationsR, coords = c("X", "Y"), crs= 4326)

## Add study type [Pest control]
MergPROD_sf1<- MergPROD_sf %>% filter(is.na(POLL_IND))%>% 
  mutate(Study_type= "Pest_enemy")

## Add study type [Pollination]
MergPROD_sf2<- MergPROD_sf %>% filter(!is.na(POLL_IND))%>% 
  mutate(Study_type= "Poll_service")

## Bind data
MergPROD_sf<- rbind(MergPROD_sf1, MergPROD_sf2)


## Load world countries shapefile
World<- st_read("~/R01_Course_Files/GRA/World_Countries__Generalized_.shp")
```



###  Distribution of reanalyzed crop field data. (Fig. 1)
```{r}
tm_shape(World) +
   tm_polygons(col = NA, midpoint = NA, 
               title = "Countries", legend.show = FALSE)+ 
   tm_shape(MergPROD_sf) +
   tm_dots("Study_type", size = 0.3, shape = 19, 
           title = "Crop fields", labels = c("Pest enemy" ,"Pollination"),
           palette = c("brown", "black"))+
   tm_layout(legend.outside = FALSE, legend.position = c("left", "center"))

```



### Save Map
```{r, eval= FALSE}
# Write to tiff
tmap_save(maps, "Context_Map.tiff", width = 8, height = 6, units = "in", dpi=300)
```
