---
title: "Soil Data Extraction Codes"
author: "Michael Madin & Kate Nelson"
date: "2022-11-05"
output: html_document
---

This is the codes for the published article. Effects of landscape simplicity on crop yields: A reanalysis of global dataset. Cite this codes as Madin, M. B., & Nelson, K. S. (2023). Effects of landscape simplicity on crop yield: A reanalysis of a global database. Plos one, 18(12), e0289799. Or access the publication at https://doi.org/10.1371/journal.pone.0289799

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo= TRUE, message= FALSE, warning= FALSE, cache= FALSE)
```


# Required packages 
```{r }
library(tidyverse)  # For processing simple files 
library(summarytools) # For summary stats
library(sjstats)    # estimate partial effect size
library(ggplot2)    # For making plots
library(kableExtra) # For creating tables
library(sf)         # For processing shape files (sf) objects
library(raster)     # For processing raster objects
library(sp)         # For handling large raster files
library(exactextractr) # for faster raster data extraction
library(readxl)       # For loading excel files
library(s2)           # For buffering un-projected geometry
```


# Importing the data and shape file
```{r}
#  Load experimental study or region locations coordinate data
Location1<- st_read("~/R01_Course_Files/Cities_Update.shp")

# Regions locations Area and Length
Areas_Regions <- read_excel("~/R01_Course_Files/Areas_Regions.xlsx")

# Load Soil data variables from the World Harmonized Soil database
Soil_Data<- readRDS("~/R01_Course_Files/GRA/HWSD_data.rds")


# Load raster Soil mapping units data from the World Harmonized Soil database
Soil_raster<- raster("~/R01_Course_Files/GRA/hwsd.bil")

# World shapefiles
World<- st_read("~/R01_Course_Files/GRA/World_Countries__Generalized_.shp")
```


## Join Rgion Area and length of Regions to Coordinate Locations
```{r }
# Combine Area of the regions and coordinate locations
LocationsR<- left_join(Areas_Regions, Location1, by= ("Name"))
  
# rearrange columns
LocationsR<- LocationsR[, c(1, 2, 5, 3, 4, 6, 7, 8)]

# Convert into sf dataframe
LocationsR_sf<- st_as_sf(LocationsR, coords = c("X", "Y"), crs= 4326)
```


## Create Buffer Around Regions

```{r }
# Create buffer for un_projected coordinates based on each region area
Locations_RB = s2_buffer_cells(LocationsR_sf, distance = (LocationsR$length_M))

# Convert into sf dataframe
LocationsRB_sf<- st_as_sf(Locations_RB, crs = st_crs(4326))

# Join the buffered geometry to region location data
LocationsRB_sf<- st_join(LocationsRB_sf, LocationsR_sf)
```


## Plot the buffered areas

```{r}
# Plot to visualized the buffered areas
ggplot() + geom_sf(data = World) +
  geom_sf(data=LocationsRB_sf, aes(color=length_M, size=length_M)) + 
  ggtitle("Region length_M")+
  theme_minimal()+
   geom_sf_text(data=LocationsRB_sf, aes(label= Region), size= 2.5)
 
```

## Rasterize Each Soil Variable

### Project the soil raster file

```{r eval=FALSE, include=TRUE}
# Project the soil mapping unit raster file
proj4string(Soil_raster) <-"+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

# Check the projects
str(Soil_raster)
```


### Rasterize Top soil USDA texture class 

```{r eval=FALSE, include=TRUE}

# Joining Top soil USDA texture class from raster data file to the list by MU_GLOBAL id
TSusda_tex2 <- subs(Soil_raster, Soil_Data %>% 
                  dplyr::select(MU_GLOBAL, T_USDA_TEX_CLASS) %>% 
                    arrange(desc(T_USDA_TEX_CLASS)) %>%
                  dplyr::distinct(MU_GLOBAL, .keep_all=TRUE), by="MU_GLOBAL")

# Save the raster data
writeRaster(TSusda_tex2, "TSusda_tex2.tif")
```


### Plot the Rasterized Top soil USDA texture class 
 
```{r}
# Visualize soil texture
spplot(TSusda_tex2, main="Top soil texture", col.regions=topo.colors(64),
       scales=list(draw = TRUE))
```


## Extract the Top soil USDA texture class

### Extract the Soil Texture Codes

```{r eval=FALSE, include=TRUE}
# Extract Top soil USDA texture class Using exact_extract package and fun = mode
Tusda_texCod<- exact_extract(TSusda_tex2, LocationsRB_sf, fun = "mode",
                           force_df = TRUE)
```

### calculate Percent Top soil USDA texture class code

This function calculate the percentage area  (i.e., number of pixels of a given texture class/ total pixels) of each texture class within each of the study region. This process help select the texture class that well represent the entire region.


```{r eval=FALSE, include=TRUE}

# Create a summarizing function to calculate pecentage base on pixel counts
sum_cover <- function(x){
  list(x %>%
    group_by(value) %>%
    summarize(total_area = sum(coverage_area)) %>%
    mutate(proportion = (total_area/sum(total_area))*100))}

# Create function
Extract_PLUse<- function(x, y){

Tusda_texCodp<- exact_extract(x, y, coverage_area = TRUE, summarize_df = TRUE,
                                fun = sum_cover) ## Extract total pixels Using fun = mode


names(Tusda_texCodp) <- LocationsRB_sf$Area_SqKm ## add unique ID to the output list


Tusda_texCodPer <- bind_rows(Tusda_texCodp, .id = "Plot_buffer") ## Make list a df

# Rename the columns
names(Tusda_texCodPer)<- c("Area_SqKm", "Tusda_texCod", "total_area", "Percent_TCod")


return(Tusda_texCodPer) ## Save extracted data into the environment

}

```


### Run the Function to Extract Percentages

```{r}
# Extract the percentage of each texture classes within study area
Tusda_texCodPer<- Extract_PLUse(TSusda_tex2, LocationsRB_sf)

# Save Data
write.csv(Tusda_texCodPer, "Tusda_texCodPer.csv")
```


## Merge soil data with the study sites

```{r eval=FALSE, include=TRUE}
# column bind the data
Soil_NDat<- cbind(LocationsRB_sf, Tusda_texCod)

```


### Add the Text Names of USDA texture classes to the codes 

The names and codes are provided in https://www.fao.org/3/aq361e/aq361e.pdf on page 13

```{r eval=FALSE, include=TRUE}
# Add actual land use for 2021 into extracted data
  Soil_NDat<- Soil_NDat%>% 
  mutate(Tsusda_Tex= 1,
         Tsusda_Tex= ifelse(mode== 9,  "loam", Tsusda_Tex),
         Tsusda_Tex= ifelse(mode== 11,  "sandy loam", Tsusda_Tex),
         Tsusda_Tex= ifelse(mode== 10,  "sandy clay loam", Tsusda_Tex),
         Tsusda_Tex= ifelse(mode== 12,  "Loamy Sand", Tsusda_Tex),
         Tsusda_Tex= ifelse(mode== 13,  "Sand", Tsusda_Tex),
         Tsusda_Tex= ifelse(mode== 3,  "clay", Tsusda_Tex))

# rearrange columns
Soil_NDat<- Soil_NDat1[, c(1:8, 10, 9)]
```


### Rename the columns

```{r eval=FALSE, include=TRUE}
# Rename the columns
names(Soil_NDat)<- c("Name", "Region", "Country", "Area_SqKm", "length_M",
                     "Tsoil_OC", "Ssoil_OC", "Tusda_texCode", "Tusda_texName",
                     "geometry")

# Convert file to data frame
Soil_NDat<- as.data.frame(Soil_NDat)

```

### Save data

```{r eval=FALSE, include=TRUE}
# Export data
write.csv(Soil_NDat, "Locations_Nsoil.csv")
```

